%----------Highschool Experience-----------
\section{Further Highschool Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{STEM Programs and Workshops}}{2017 -- 2019}
        \resumeItemListStart
          \resumeItem{MINT-EC Workshop: Masterclass Particle Physics (Jun. 2019).}
          \resumeItem{Fraunhofer Talent Take Off - Vernetzen (2019).}
          \resumeItem{Regional MINT-Camp “Life on Mars” (May--Jun. 2019): Developed concepts for life-essential resources.}
          \resumeItem{Tag der Kombinatorik — group-based local math contest (Feb. 2019).}
          \resumeItem{Student Engineer Academy — project track (2018--2019).}
          \resumeItem{Fraunhofer Talent School (Mar. 2018): Implemented an image classifier (cats vs. dogs).}
          \resumeItem{Student Engineer Academy — Programming in C (2017--2018).}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Early student Internships}}{2015 -- 2019}
        \resumeItemListStart
          \resumeItem{Bosch, Stuttgart-Feuerbach — voluntary engineering internship (Apr., 2019).}
          \resumeItem{Palfinger, Ilsfeld — voluntary mechanic internship (Sep. -- Oct., 2017).}
          \resumeItem{Getrag, Untergruppenbach — voluntary mechanic internship (Sep., 2017).}
          \resumeItem{Vector, Stuttgart — “Mitmachen Ehrensache” social one-day placement (Dec., 2015).}
          \resumeItem{Eberhard Schweizer Grundschule Ganztagesgruppe — social week-long placement in nursery school (Nov., 2015).}
        \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Music and Community}}{2009 -- 2020}
          \resumeItemListStart
          \resumeItem{Leadership: Youth spokesman, Heinriet Sports Club (2016--2020); school mediator for grades 5--6 (2016--2020).}
          \resumeItem{Awards: D2 (2017, excellent--very good); Jugend musiziert 2nd prize (2015); D1 (2014, very good); scholarship (2013) and gifted promotion (2012) in trombone.}
          \resumeItem{Piano and trombone (advanced); District youth orchestra Heilbronn (2017--2020); Musikverein Heinriet (2014--2020); school band 1st trombone (2012--2014).}
          \resumeItem{Theater: Castle theater productions as trombonist and actor (2017: Das kleine Gespenst; 2016: Some like it hot).}
          \resumeItemListEnd

  \resumeSubHeadingListEnd
