%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{\href{https://github.com/EmanuelMedinaAraujo/ClarissaApp}{ClarissaApp}} $|$ \emph{Privacy-first personal health mobile app}}{Aug. 2025 -- Present}
        \resumeItemListStart
          \resumeItem{Built a privacy-first mobile app with React Native (Expo) and TypeScript for menstrual cycle tracking.}
          \resumeItem{Implemented calendar-based cycle logging with symptom tracking and three themes (dark/light/red).}
          \resumeItem{Engineered offline-first storage with expo-sqlite, modular components/hooks, and a clear UX for fast daily logging.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{\href{https://github.com/EmanuelMedinaAraujo/check24-comparison-challenge}{Full-Stack ISP Comparison}} $|$ \emph{Check24 Scholarship Challenge}}{May 2025 -- Jun. 2025}
        \resumeItemListStart
            \resumeItem{Implemented a modular full-stack (React + Vite + Tailwind frontend, Node.js/Express backend).}
            \resumeItem{Integrated timeout/health handling and an ISP provider normalization layer to produce consistent comparisons.}
            \resumeItem{Developed a share results feature with via a TinyURL export persisting the results within the link.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Learning Based Inverse Kinematics} $|$ \emph{Bachelor Thesis}}{Jun. 2024 -- Nov. 2024}
        \resumeItemListStart
          \resumeItem{Designed and implemented learning-based IK solvers for 2- and 3-DOF manipulators, comparing direct-angle regression with probabilistic outputs across MLP, LSTM, hybrid MLP+LSTM, and PPO.}
          \resumeItem{Built a synthetic data generation and evaluation pipeline; ran controlled experiments on a 10k-sample test set to quantify accuracy, convergence, and runtime across architectures and output parameterizations.}
          \resumeItem{Found that a simple MLP with direct-angle prediction consistently outperformed more complex models, highlighting a non-trivial complexity-performance trade-off and yielding clear guidance for practical IK model selection.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Ironman} $|$ \emph{2.8km swim, 180km bike, 42.2km run; Overall Time : 14:21:26h}}{Oct. 2022 -- Aug. 2024}
        \resumeItemListStart
          \resumeItem{Completed full Ironman triathlon through disciplined training and a goal-oriented race plan, demonstrating resilience and on-the-fly problem-solving under fatigue and variable race conditions to reach the finish.}
        \resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{Ilab2} $|$ \emph{Advanced Practical Networking Course}}{Oct. 2023 -- Mar. 2024}
        \resumeItemListStart
          \resumeItem{Completed course labs on advanced networking topics in a two-person team, building strong proficiency in GNU/Linux CLI and Cisco IOS for complex network configurations.}
          \resumeItem{Co-created a full WebAuthN lab from scratch (lecture + prelab + hands-on) covering passkeys, FIDO2/WebAuthN flows, and security keys, enabling peers to configure WebAuthN end-to-end.}
          \resumeItem{Engineered the practical stack with Keycloak and a Spring Boot demo app, guiding students through server setup, WebAuthN policy configuration, and packet analysis to deepen protocol understanding.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Cyber-Physical Systems Survey} $|$ \emph{Advanced Cyber-Physical Seminar}}{Apr. 2023 -- Jul. 2023}
        \resumeItemListStart
          \resumeItem{Produced an in-depth research survey of numerical inverse kinematics in cluttered environments for robots.}
          \resumeItem{Evaluated Jacobian-based, heuristic, and meta-heuristic methods, for convergence, robustness, and performance.}
        \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/ManuelLerchner/FreshFinder}{FreshFinder}} $|$ hackaTUM - HelloFresh Challenge}{Nov. 2023}
        \resumeItemListStart
          \resumeItem{Developed a React + TypeScript web app for collaborative, parallel cooking sessions with a team of 4}
          \resumeItem{Designed a recipe dependency-graph architecture for task distribution using Supabase Realtime.}
          \resumeItem{Integrated the OpenAI API to dynamically adapt recipes for individual preferences and amounts.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{\href{https://devpost.com/software/streamtinder}{StreamFindA}} $|$ hackaTUM - Burda Challenge}{Nov. 2022}
        \resumeItemListStart
          \resumeItem{Built a React front end with a Django/Python backend for swipe-based movie/series recommendations.}
          \resumeItem{Implemented a recommendation algorithm based on pairwise choices using dwell time and negative feedback.}
          \resumeItem{Parsed and normalized the provided multi-platform catalog to a usable format to power reliable recommendations.}
        \resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{Computer Architecture Practical Course} $|$ \emph{Advanced Practical Course}}{Apr. 2021 -- Jul. 2021}
        \resumeItemListStart
          \resumeItem{Implemented iterative space-filling Z-curve generators in assembly with SVG export and performance benchmarks.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Humanoid-controlled robot arm} $|$ \emph{Student Engineering Academy}}{Sep. 2018 -- Jul. 2019}
        \resumeItemListStart
          \resumeItem{Programmed a self-built robot arm controlled via a humanoid interface.}
          \resumeItem{Developed a virtual movement visualization of the arm sleeve with flex sensors in Blender with Python.}
          \resumeItem{Programmed Arduino microcontroller in C/C++ to read movement data from the arm sleeve, transmit them wirelessly via radio using the SPI protocol to the robot arm and map them to the servo motors.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{MATLAB physics visualizations} $|$ \emph{International Summer Physics Institute, University of Notre Dame}}{Jul. 2018}
        \resumeItemListStart
          \resumeItem{Completed Cosmic Ray Detection team project by building a detector plus analyzing and visualizing the data.}
          \resumeItem{Visualized and analyzed CERN CMS particle-physics data using MATLAB.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Hydrogen fuel cell prototype} $|$ \emph{9th Trinational Student Congress, Strasbourg}}{Jan. 2017}
        \resumeItemListStart
          \resumeItem{Developed a hydrogen fuel cell concept and demonstrator with a friend and presented it in the congress.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
